MCMC Redistricting

### 2020-12-13 paper.Rmd
new section

Now we can look at the bias asscoiated with our simulations. Our simulation consisted of 10,000 different and unique redistricting maps that the algorithm computed using our parameters and equal population constraints. For voting data we fed the algorithm the results for the goverenors election. Each point on the graph is a distinct Colorado district map. On X-axis we have the percentage of precincts swapped for a particular simulation. On the Y axis we have our calculated political bias. The red dotted line shows 0 bias, above that line is democratic bias and below that line is republican bias. The black line shows the current political bias which is slightly democratic.

@@

>>>>

Now we can look at the bias asscoiated with our simulations. Our simulation consisted of 10,000 different and unique redistricting maps that the algorithm computed using our parameters and equal population constraint. Each point on the graph is a distinct Colorado district map. On the X-axis we have the percentage of precincts swapped for a particular simulation. On the Y-axis we have our calculated political bias. The red dotted line shows 0 bias, above that line is democratic bias and below that line is republican bias. The black line shows the current political bias which is slightly democratic.

@@

## Moving Forward

Moving forward we would like to exlpore the compactness constraint to attempt to get a more realistic redistricted map of Colorado. Also bumping up the number of simulations could prove to be useful, our limit with the computers that we have is 10,000 runs getting that number up to 100,000 would be ideal. However being able to do those two things woiuld require access to more powerful computers. Also running this analysis on another state could be very interesting, Texas for example, a historically republican state, has shown a trend of democratic voting increase. It would be very interesting to look into how gerrymandering has been affecting Texas politics.
